Conversations in time: interactive visualization to explore structured temporal data

### 2020-07-19 tsibbletalk.Rmd
bullet points
outline sections

>>>>

* An ensemble of graphics
* Accelerate the exploratory data visualization process

# Background

## Interactive visualization systems with linking views

* {ggobi} and {xggobi}
* {cranvas} and {cranvastime}
* [crossfilter.js](http://crossfilter.github.io/crossfilter/)
* {crosstalk} and html widgets

## Tidy temporal data and workflow

* {tsibble}
* and tsibble-centered workflow

# Shared temporal data for coordinated views

* Symbolic formula to express structural specifications among keyed units, using `/` and `*` from Wilkinson notation (10.2307/2346786) for nesting and crossing.
* Nesting variables generate hierarchical tree, hence `plotly_key_tree()`. Overview and navigation made easier.
* One-to-many linking: marking a single point of interest highlights all other points that share particular data values (connect-type)
* Lists of key values, and json
* R6 subclass of `SharedData` from {crosstalk}

# Slicing and dicing time

* Time wrapping: absolute time to relative time, grouped by corresponding lower-resolution time. date-times -> hours, by dates
* Transform and send newly-transformed data via server, without updating anything else (e.g. layout and graphical elements), to avoid completely redrawing.
* A shiny module: slider and plot

# Case study: monthly domestic tourist trips in Australia

# Conclusions and discussions

# References {-}
